Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-03-13 WRITEUP/ms.tex
moved Sec on Q to discussion.

\subsection{Structure identification}\label{sec:method}

@@

The mass of an MC is calculated from the uniformly-gridded 3D density field, integrating over the MC volume $V$. The effective size is defined assuming spherical geometry, i.e. $R \equiv (3 V /4 \pi)^{1/3}$.
%
The velocity dispersion of MCs is calculated from non-thermal velocity dispersion ($\sigma_{\rm NT}$) and thermal sound speed ($c_s$):
\begin{equation}
\sigma^2 = \sigma_{\rm NT}^2 + c_s^2.
\label{eqn:veldisp}
\end{equation}
% 
In \obs of MC, the linewidths contribution of dense gas contribution is larger then the one from the diffuse gas. We therefore calculate 
each term on the RHS of Equation~\ref{eqn:veldisp} as a density-weighted quantity. For instance, the non-thermal velocity dispersion is 
calculated as follows:
\begin{equation}
\sigma_{\rm NT}^2 = \frac{1}{{3}}\frac{\sum_{i} \rho_i \left|\mathbf{v}_i - \mathbf{\bar v}\right|^2}{\sum_i \rho_i}\,,
\end{equation}
where the sum is done for the cells composing each MC.
The local sound speed of all identified molecular complexes are much smaller compared to the their turbulent velocities\footnote{We find comparable velocity dispersion between that derived from taking the root mean square versus that derived from thermal and non-thermal pressure terms, indicating that rotation velocity is unlikely to be the dominant source of velocity dispersion reported here.}. On average, the Mach number of the MCs corresponds to about $\mathcal{M} = \sigma_{\rm NT}/c_s\approx 50$. This is consistent with the global analysis done on \flower by \citet{Vallini18a}.

@@

%\subsection{Gravitational Instabilities}\label{sec:Q}
\subsection{Toomre stability}\label{sec:Q}

@@

For the purpose of this work, we present Toomre $Q$ map in \Sec{results} and discuss the importance of support from galactic rotation and shear against axisymmetric perturbations in \Sec{origin}.

@@

\begin{figure*}
\centering
\includegraphics[trim=5 5 8 8, clip, width=0.515\textwidth]{\figpath/ss16_larsons.png}
\includegraphics[trim=50 5 5 6, clip, width=0.472\textwidth]{\figpath/ss27_larsons.png}
\includegraphics[trim=5 5 8 8, clip, width=0.515\textwidth]{\figpath/ss16_alphavir.png}
\includegraphics[trim=50 5 5 6, clip, width=0.472\textwidth]{\figpath/ss27_alphavir.png}
\includegraphics[trim=5 5 8 8, clip, width=0.512\textwidth]{\figpath/ss16_PVE.png}
\includegraphics[trim=50 5 5 6, clip, width=0.472\textwidth]{\figpath/ss27_PVE.png}
\caption{
Linewidth-size relation (top), 
{\bf .... (middle), and blah blah (bottom)}
for MCs (star symbols) 
identified in the two most extreme evolutionary stages of \flower\ --- accreting phase (left) and starburst phase (right).
Star symbols are color-coded by the density thresholds ($n_{\rm cut}$).
\AP{ have not found a good clipping for the upper left panel} 
\AP{please 1) increase a bit the size of the labels 2) put the legend only the right panels 
3) add a text label to the upper left corner, to ditinguish between accreting and starburst stage 
4) I would use a perceptually increasing colorbar to indicate the different cuts 
5) legend for the cuts can be substituted by a colorbar axis to be shown as an inset in 1 of the panels or as a separate figure below the panels}
\label{fig:alpha16-28}}
\end{figure*}

@@

\subsection{Single evolutionary stage}  \label{sec:singless}

For each of the two most extreme evolutionary stages of \flower\ --- accretion and starburst phase (see \Sec{sfh}), we identify a set of MCs.
%
Scaling relations for the MCs identified in the accretion phase are shown in top panels of \Fig{larsons_single}, \Fig{alpha16}, and \Fig{alpha27}, and in the bottom panels for the starburst phase.
%
Regardless of the H$_2$ density cuts adopted, the MCs are found to have consistently \AP{which is already said in the last part of previous Sec.; I would put here that part} \DL{?}
high turbulences and surface densities in both stages. These correspond to MCs at the center of the main disk of \flower and occupy the top right corner of the Larson's relation shown in \Fig{larsons_single}.
%
As we increase the density threshold, some of the MCs within the main disk break into multiple sub-MCs. As such, we effectively identify a population of denser molecular structures (see \Fig{MC}).

% PVE
We also compare the MCs identified in our simulations to those observed in the Milky Way in the context of the $\sigma^2/R - \Sigma$ relation (see \Fig{alpha27}). The dashed lines in the figure show the loci along which the given external pressures are needed for MCs to have linewidth for a given set of surface densities (see \Sec{PVE}).
% (Rice+16) find variation in $V_0^2$, where they find larger linewidths for GMCs in inner galactic disk, but they find that the clouds in the Galactic disk are still consistent with SVE (see also Solomon87a ; cf. Heyer+09).
The MCs in the satellite galaxies are found to follow the locus of $\log{(P/\textrm{K cm}^{-3})}$\eq6 (see \Fig{alpha27}), which 
is consistent with that found for the bulk of dense gas in the simulation in the phase-space analysis presented in \citet{Pallottini17a}.

\subsection{Temporal evolution and cut dependence}\label{sec:ncut}
% single Snapshot
We investigate possible variations in the dynamics of the molecular structures of \flower and its satellites to test the robustness of our results against the choice of density threshold by adopting
different sets of $n_{\rm cut}$ in identifying the MCs.
%
That is, how sensitive are the structure properties, and thus, the results presented in \Sec{singless} dependent on the choice of density thresholds. We vary the choice of H$_2$ density for each of the evolutionary stages and find no obvious differences in our results (i.e., inferences on the dynamics of \z$\sim$\,6 MCs in relation to those observed in nearby and \z$\sim$2 galaxies in the context of
cloud scaling relations).
%
In addition, for the densest MC in the main disk of \flower, we find that while its size decreases as we increase $n_{\rm cut}$ --- as one would intuitively expect, the velocity dispersion remain approximately $\sigma\simeq$\,200\,\kms (see also \Fig{larsons_single}).
%
This lack of variation is reassuring, in the sense that at least on the scales studied here, the dynamics of the MCs are not artifacts or biased by our choice of $n_{\rm cut}$. Our results are therefore robust to the various density cuts of choice.

\begin{comment}
\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16_larsons.png}
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss27_larsons.png}
\caption{
Larson's (linewidth-size) relation of \flower in
accretion phase (top) and
starburst phase (bottom) compared to
those observed in nearby and the \z$\sim$2 star-forming galaxy.
% Red lines show the relation obtained from \citet{}.
Observed data and empirical relations are compiled from \citet{Larson81a, Heyer04a, Rosolowsky05a, Bolatto08a, Swinbank11a, Leroy15a}.
\label{fig:larsons_single}}
\end{figure*}

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/ss16_alphavir.png}
\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/ss27_alphavir.png}
\caption{
Virial parameter and cloud mass of \flower (star symbols) in the accretion phase (top panel) 
and the starburst phase (bottom panel) compared to the 
Milky Way (other symbols).
Literature data are compiled from \citealt{Kauffmann17b} and references therein.
Star symbols are color-coded by $n_{\rm cut}$.
Star symbols lying close to $\alpha_{\rm vir}\approx2$ correspond to MCs in the satellite galaxies.
\label{fig:alpha16}}
\end{figure*}

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/ss16_PVE.png}
\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/ss27_PVE.png}
\caption{
$\sigma^2/R - \Sigma_{\rm gas}$ relation of the MCs identified in our simulation (star symbols)
in the accretion phase (top panel) and the starburst phase (bottom panel)
compared to those observed in the Milky Way (black dot markers; \citealt{Heyer09a}).
The V-shaped dashed lines show the loci along which the given external pressures
are needed for MCs to have linewidth $\sigma$ for a given set of surface densities (see \Sec{PVE}).
Similar to \Fig{alpha16}, star symbols are color-coded by $n_{\rm cut}$.
Star symbols along the locus of $\log{(P/\textrm{K cm}^{-3}) = 6}$
correspond to MCs in the satellite galaxies.
\label{fig:alpha27}}
\end{figure*}
\end{comment}

@@

We show in \Fig{MR} the size-mass relation of the MCs of \flower compared to observational data of molecular clouds in the Milky Way that are found to be associated with massive \SF \citep{Beuther02a, Mueller02a, Hill05a, Motte07a} and an empirical relation obtained for massive \SF based on Milky Way clouds ($<$10\,\Msun; \citealt{Kauffmann10b, Kauffmann10c} and references therein): $M \gtrsim 870$\,\Msun$\times\,\left(r/{\rm pc}\right)^{1.33}$.
%
In the same plot, we also show loci of constant surface densities, which are parameterized through the visual extinction $A_V$. As shown in \Fig{MR}, the MCs identified in \flower lie above this relation, along the locus with a visual extinction of $A_V$\eq4\,mag \citep{Lombardi10a}. We discuss this result in the following section.

@@

Maps of the Toomre $Q$ parameters for the gas, stars, and the effective two-component $Q_{\rm eff}$ are shown in \Fig{Q} 
(see also \Fig{h2density} for an example of MCs identified in this evolutionary stage of \flower
for different $n_{\rm cut}$). Fragmentation are expected in regions of low Toomre $Q$ values.
 \AP{why then we do not postpone the figure presentation?} \DL{I am not sure if I should first show all the plots in Sec 4 and the discuss in details in Sec 5 or what. I guess we could just show
in Sec 5.}
We discuss the importance of accounting for stellar contributions and the effect of the thickness of the disk to the total stability criterion. 
Close resemblance of the $Q_{\rm eff}$ and $Q_{\star}$ maps indicates that contributions from the stellar component play an important role in 
governing the stability of the MCs against $m$\eq0 perturbations.
This can be understood since stars in \flower dominates in mass in the central part of the galaxy, 
so their gravitational potential provides a non-negligible contribution to the stability. 
Similarly, contribution from the thickness of the disk is important in \flower since its disk is not thin (with a 
scale height ratio of $h/r_{\rm gal}$\ssim150\,pc/1\,kpc\,$\simeq$\,0.15) and since \flower is more of a warped disk.
That is, some MCs are located in regions of $Q_{\rm gas}$\ssim1, but 
when including the effects of stars and thickness of the disk (via $\sigma_z$),
they are consistent with $Q_{\rm gas} > 1$.
Further interpretation and implication of this is discussed in \Sec{origin}.

@@

We thank Jens Kauffmann, Thushara Pillai, and Mark Swinbank for sharing their data.
%
TKDL acknowledges support by the NSF through award SOSPA4-009 from the NRAO and support from the Simons Foundation.
%
AF acknowledges support from the ERC Advanced Grant INTERSTELLAR H2020/740120.
%
This work is based on a project developed at the Kavli Summer Program in Astrophysics (KSPA) held at the Center for Computational Astrophysics of the Flatiron Institute in 2018. The program was co-funded by the Kavli Foundation and the Simons Foundation.
%
We thank the KSPA Scientific and Local Organizing Committees, and the program founder, Pascale Garaud, for supporting the genesis of this work.
%
We also thank the Center for Cosmology and Particle Physics at the New York University for their hospitality in hosting us after the steam pipe explosion in NYC during the KSPA.
%
This research has made use of NASA's Astrophysics Data System Bibliographic Services.
%
We acknowledge use of the Python programming language \citep{VanRossum1991}, Astropy \citep{astropy}, Cython \citep{behnel2010cython}, Matplotlib \citep{Hunter2007}, NumPy \citep{VanDerWalt2011}, \ncode{Pymses} \citep{Labadens2012}, SciPy \citep{scipyref}, and \ncode{yt} \citep{Smith09a,Turk2011a}.
%
%and \ncode{yt}, a community-developed Python package for analyzing simulation data in Astronomy.

>>>>

\subsection{Structure Identification}\label{sec:method}

@@

The mass of an MC is calculated from the uniformly-gridded 3D density field, integrating over the MC volume $V$. The effective size is defined assuming spherical geometry, i.e. $R \equiv (3 V /4 \pi)^{1/3}$.
%
The velocity dispersion of MCs is calculated from non-thermal velocity dispersion ($\sigma_{\rm NT}$) and thermal sound speed ($c_s$):
\begin{equation}
\sigma^2 = \sigma_{\rm NT}^2 + c_s^2.
\label{eqn:veldisp}
\end{equation}
% 
In \obs of MC, the linewidths contribution of dense gas contribution is larger then the one from the diffuse gas. We therefore calculate 
each term on the RHS of Equation~\ref{eqn:veldisp} as a density-weighted quantity. For instance, the non-thermal velocity dispersion is 
calculated as follows:
\begin{equation}
\sigma_{\rm NT}^2 = \frac{1}{{3}}\frac{\sum_{i} \rho_i \left|\mathbf{v}_i - \mathbf{\bar v}\right|^2}{\sum_i \rho_i}\,,
\end{equation}
where the sum is done for the cells composing each MC.
The local sound speed of all identified molecular complexes are much smaller compared to the their turbulent velocities\footnote{We find comparable velocity dispersion between that derived from taking the root mean square versus that derived from thermal and non-thermal pressure terms, indicating that rotation velocity is unlikely to be the dominant source of velocity dispersion reported here.\label{ftn:veldisp}}. 
On average, the Mach number of the MCs corresponds to about $\mathcal{M} = \sigma_{\rm NT}/c_s\approx 50$. This is consistent with the global analysis done on \flower by \citet{Vallini18a}.

@@

%\subsection{Gravitational Instabilities}\label{sec:Q}
\subsection{Toomre Stability}\label{sec:Q}

@@

For the purpose of this work, we present Toomre $Q$ maps in \Sec{results} and discuss the importance of support from galactic rotation and shear against axisymmetric perturbations in \Sec{origin}.

@@

\begin{figure*}
\centering
\includegraphics[trim=5 5 8 8, clip, width=0.515\textwidth]{\figpath/ss16_larsons.png}
\includegraphics[trim=50 5 5 6, clip, width=0.472\textwidth]{\figpath/ss27_larsons.png}
\includegraphics[trim=5 5 8 8, clip, width=0.515\textwidth]{\figpath/ss16_alphavir.png}
\includegraphics[trim=50 5 5 6, clip, width=0.472\textwidth]{\figpath/ss27_alphavir.png}
\includegraphics[trim=5 5 8 8, clip, width=0.512\textwidth]{\figpath/ss16_PVE.png}
\includegraphics[trim=50 5 5 6, clip, width=0.472\textwidth]{\figpath/ss27_PVE.png}
\caption{
Linewidth-size relation (top), 
{\bf .... (middle), and blah blah (bottom)}
for MCs (star symbols) 
identified in the two most extreme evolutionary stages of \flower\ --- accreting phase (left) and starburst phase (right).
Star symbols are color-coded by the density thresholds ($n_{\rm cut}$).
\AP{ have not found a good clipping for the upper left panel} 
\AP{please 1) increase a bit the size of the labels 2) put the legend only the right panels 
3) add a text label to the upper left corner, to ditinguish between accreting and starburst stage 
4) I would use a perceptually increasing colorbar to indicate the different cuts 
5) legend for the cuts can be substituted by a colorbar axis to be shown as an inset in 1 of the panels or as a separate figure below the panels}
\label{fig:larsons_single}}
\end{figure*}

@@

\subsection{Single Evolutionary Stage}  \label{sec:singless}

For each of the two most extreme evolutionary stages of \flower\ --- accretion and starburst phase (see \Sec{sfh}), we identify a set of MCs.
%
Scaling relations for the MCs identified in the accretion phase are shown in left panels of \Fig{larsons_single} and in the right 
panels for the starburst phase.
%
Regardless of the H$_2$ density cuts adopted, the MCs are found to have consistently \AP{which is already said in the last part of previous Sec.; I would put here that part} \DL{?}
high turbulences and surface densities in both stages. These correspond to MCs at the center of the main disk of \flower and occupy the top right corner of the Larson's relation shown in \Fig{larsons_single}.
%
As we increase the density threshold, some of the MCs within the main disk break into multiple sub-MCs. As such, we effectively identify a population of denser molecular structures (see \Fig{MC}).

% PVE
We also compare the MCs identified in our simulations to those observed in the Milky Way in the context of the $\sigma^2/R - \Sigma$ relation (see bottom panels of \Fig{larsons_single}). Dashed lines in the figure show the loci along which the given external pressures are 
needed for MCs to have certain linewidths for a given set of surface densities (see \Sec{PVE}).
% (Rice+16) find variation in $V_0^2$, where they find larger linewidths for GMCs in inner galactic disk, but they find that the clouds in the Galactic disk are still consistent with SVE (see also Solomon87a ; cf. Heyer+09).
The MCs in the satellite galaxies are found to follow the locus of $\log{(P/\textrm{K cm}^{-3})}$\eq6, which 
is consistent with that found for the bulk of dense gas in the simulation in the phase-space analysis presented in \citet{Pallottini17a}.

@@

We show in \Fig{MR} the size-mass relation of the MCs of \flower compared to observational data of molecular clouds in the Milky Way that are found to be associated with massive \SF \citep{Beuther02a, Mueller02a, Hill05a, Motte07a} and an empirical relation obtained for massive \SF based on Milky Way clouds ($<$10\,\Msun; \citealt{Kauffmann10b, Kauffmann10c} and references therein): $M \gtrsim 870$\,\Msun$\times\,\left(r/{\rm pc}\right)^{1.33}$.
%
In the same plot, we also show loci of constant surface densities, which are parameterized through the visual extinction $A_V$. As shown in \Fig{MR}, the MCs identified in \flower lie above this relation, along the locus with a visual extinction of $A_V$\eq4\,mag \citep{Lombardi10a}. We discuss this result in the Discussion section.

@@

\subsection{Temporal Evolution and Adopted Density Threshold Dependence}\label{sec:ncut}
% single Snapshot
We investigate possible variations in the dynamics of the molecular structures of \flower and its satellites to test the robustness of our results against the choice of density threshold by adopting
different sets of $n_{\rm cut}$ in identifying the MCs.
%
That is, how sensitive are the structure properties, and thus, the results presented in \Sec{singless} dependent on the choice of density thresholds. We vary the choice of H$_2$ density for each of the evolutionary stages and find no obvious differences in our results (i.e., inferences on the dynamics of \z$\sim$\,6 MCs in relation to those observed in nearby and \z$\sim$2 galaxies in the context of
cloud scaling relations).
%
In addition, for the densest MC in the main disk of \flower, we find that while its size decreases as we increase $n_{\rm cut}$ --- as one would intuitively expect, the velocity dispersion remain approximately $\sigma\simeq$\,200\,\kms (see also \Fig{larsons_single}).
%
This lack of variation is reassuring, in the sense that at least on the scales studied here, the dynamics of the MCs are not artifacts or biased by our choice of $n_{\rm cut}$. Our results are therefore robust to the various density cuts of choice.

% temporal evolution in Cloud Dynamics
We show the properties of all MCs identified across all evolutionary stages in \Fig{alpha16-28}. We find no quantitative differences in the cloud properties over the 700\,Myr traced in our simulation.

%
%\begin{comment}
%\begin{figure*}[htbp]
%\centering
%\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16_larsons.png}
%\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss27_larsons.png}
%\caption{
%Larson's (linewidth-size) relation of \flower in
%accretion phase (top) and
%starburst phase (bottom) compared to
%those observed in nearby and the \z$\sim$2 star-forming galaxy.
%% Red lines show the relation obtained from \citet{}.
%Observed data and empirical relations are compiled from \citet{Larson81a, Heyer04a, Rosolowsky05a, Bolatto08a, Swinbank11a, Leroy15a}.
%\label{fig:larsons_single}}
%\end{figure*}
%
%\begin{figure*}[htbp]
%\centering
%\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/ss16_alphavir.png}
%\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/ss27_alphavir.png}
%\caption{
%Virial parameter and cloud mass of \flower (star symbols) in the accretion phase (top panel) 
%and the starburst phase (bottom panel) compared to the 
%Milky Way (other symbols).
%Literature data are compiled from \citealt{Kauffmann17b} and references therein.
%Star symbols are color-coded by $n_{\rm cut}$.
%Star symbols lying close to $\alpha_{\rm vir}\approx2$ correspond to MCs in the satellite galaxies.
%\label{fig:alpha16}}
%\end{figure*}
%
%\begin{figure*}[htbp]
%\centering
%\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/ss16_PVE.png}
%\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/ss27_PVE.png}
%\caption{
%$\sigma^2/R - \Sigma_{\rm gas}$ relation of the MCs identified in our simulation (star symbols)
%in the accretion phase (top panel) and the starburst phase (bottom panel)
%compared to those observed in the Milky Way (black dot markers; \citealt{Heyer09a}).
%The V-shaped dashed lines show the loci along which the given external pressures
%are needed for MCs to have linewidth $\sigma$ for a given set of surface densities (see \Sec{PVE}).
%Similar to \Fig{alpha16}, star symbols are color-coded by $n_{\rm cut}$.
%Star symbols along the locus of $\log{(P/\textrm{K cm}^{-3}) = 6}$
%correspond to MCs in the satellite galaxies.
%\label{fig:alpha27}}
%\end{figure*}
%\end{comment}

%
%\begin{comment}
%
%\begin{figure*}[htbp]
%\centering
%\includegraphics[trim=0 20 30 30, clip, width=0.7\textwidth]{\figpath/{ss16_gas_toomre_proj_0_zoom_2.0_kpc}.png}
%\caption{
%Maps of the total gas surface density (top left), 
%velocity dispersion (top right),
%epicyclic frequency (bottom left), 
%and Toomre $Q$ parameter (bottom right) in the $xy$-plane.
%Modest smoothing has been applied to the maps. 
%A divergent colormap is used for the Toomre $Q$ map to facilitate 
%identification of regions above and below $\log{Q_{\rm gas}}$\eq0.
%Crosses correspond to positions of MCs identified using the lowest $n_{\rm cut}$. % using 0.32
%Positions of sub-MCs are not shown (but see top row of \Fig{Qeff} for an example). 
%\label{fig:Q}}
%\addtocounter{figure}{-1}
%\end{figure*}
%
%\begin{figure*}[htbp]
%\centering
%\includegraphics[trim=0 20 30 30, clip, width=0.7\textwidth]{\figpath/{ss16_gas_toomre_proj_1_zoom_2.0_kpc}.png}
%\caption{Continued. Maps showing the various quantities projected on the $xz$-plane.}
%\addtocounter{figure}{-1}
%\end{figure*}
%
%\begin{figure*}[htbp]
%\centering
%\includegraphics[trim=0 20 30 30, clip, width=0.7\textwidth]{{\figpath/ss16_gas_toomre_proj_2_zoom_2.0_kpc}.png}
%\caption{Continued. Maps show the various quantities projected on the $yz$-plane.}
%\end{figure*}
%
%\begin{figure*}[htbp]
%\centering
%\includegraphics[trim=0 20 30 30, clip, width=0.7\textwidth]{\figpath/{ss16_star_toomre_proj_0_zoom_2.0_kpc}.png}
%\caption{
%Same as \Fig{Q} but for the stellar component, projected in the $xy$-plane.
%\label{fig:Qstar}}
%% \addtocounter{figure}{-1}
%\end{figure*}
%
%\begin{figure*}[htbp]
%\centering
%\includegraphics[trim=10 0 100 20, clip, width=0.35\textwidth]{\figpath/{ss16_toomreEff_proj_0_zoom_2.0_kpc_0.32}.png}
%\includegraphics[trim=30 0 10 20, clip, width=0.425\textwidth]{\figpath/{ss16_toomreEff_proj_0_zoom_2.0_kpc_6.81}.png}  \\
%\includegraphics[trim=10 0 0 10, clip, width=0.425\textwidth]{\figpath/{ss16_gas_SD_proj_0_zoom_2.0_kpc}.png} \\
%\includegraphics[trim=30 25 30 20, clip, width=0.4\textwidth]{\figpath/{ss16_toomreEff_proj_0_zoom_0.8_kpc_6.81}.png}
%\includegraphics[trim=10 0 0 0, clip, width=0.38\textwidth]{\figpath/{ss16_gas_SD_proj_0_zoom_0.8_kpc}.png}
%\caption{
%Effective two-component Toomre $Q_{\rm eff}$ (top row) 
%and gas surface density (middle) maps projected onto the $xy$-plane.
%Positions of MCs identified using the lowest $n_{\rm cut}$\eq0.32\,cm$^{-3}$ (top left; same as \Fig{Q})
%and $n_{\rm cut}$\eq6.81\,cm$^{-3}$ (top right) are overplotted as crosses.
%Bottom row: Effective $Q_{\rm eff}$ (left) and gas surface density (right) maps zoomed in on the central 1.5\,kpc region.
%Cross markers indicate positions of MCs identified with $n_{\rm cut}$\eq6.81\,cm$^{-3}$ (same as top right).
%Modest smoothing has been applied to the maps. 
%A divergent colormap is used for the Toomre $Q$ map to facilitate 
%identification of regions above and below $\log{Q_{\rm gas}}$\eq0.
%Some MCs lie in regions of $\log{Q_{\rm eff}}\gtrsim0$, whereas regions of $\log{Q_{\rm eff}}\lesssim0$ 
%are likely gravitationally unstable.
%\label{fig:Qeff}}
%% \addtocounter{figure}{-1}
%\end{figure*}
%%\clearpage
%
%\end{comment}

The MCs of \flower has dynamics largely similar to those observed in $z$\ssim2 spatially resolved studies of gas-rich star-forming galaxies, in terms of their velocity dispersions, sizes, and gas surface densities (\Fig{larsons_single}; see e.g., \citealt{Swinbank11a}), with sizes of the order of $R\simeq$\,100\,pc and velocity dispersions of $\sigma\simeq$\,20$-$80\,\kms.
%
% velocity dispersion, larsons
%
Their velocity dispersions are also comparable to those observed in the inner Milky way and nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a}), which lies along the locus of $\sigma\propto R^{0.56}$. Such high velocity dispersions and surface densities are expected since they are located in the nuclear regions of the galaxy, where the potential well is also deep. The higher velocity dispersions 
(see footnote~\ref{ftn:veldisp} on page \pageref{ftn:veldisp}) of these MCs can also be understood as they have experienced more recent episodes of \SF as \flower is assembling its stellar mass (these MCs also have higher stellar-to-gas mass ratios of $\sim$60).
%
In fact, by $z\simeq$\,7.2 (\AP{i would always refer to the evolutionary stage name, once in defined in Fig. 1; we might want to use italic to underline it is a definition} i.e., accretion phase; see \Fig{SFH}a), \flower has assembled a stellar mass of $M_*$\eq7.5\E{9}\,\Msun. Thus, the higher velocity dispersion is due in part to the stronger stellar feedback compared to e.g., MCs in its satellite galaxies ($\sigma\approx$10\,\kms).

% different evolutionary stages
In the scaling relations examined, we find similar MC properties in relation to those observed in the nearby Universe between the accretion phase and the starburst phase of \flower (see \Fig{larsons_single}). That is, we do not find any quantitative major differences in the MC properties between the accretion and the starburst phase, which are separated by $\simeq$300\,Myr.

\subsection{Origin and Physical Scales of MCs} \label{sec:origin}

The largest molecular structure identified is essentially the main disk of \flower and breaks down into smaller substructures that are denser as we increase $n_{\rm cut}$ (see e.g., \Fig{alpha16-28}). Overall, the MCs we identified are much bigger in size and mass than nearby GMCs, but comparable to those observed in $z$\,\ssim2$-$4 galaxies based on spatially resolved imaging \citep{Swinbank11a}.

% mass scale
Observations of nearby gas-rich galaxies such as M64 and NGC\,253 show higher velocity dispersions compared to the disk/mid-plane of the Milky Way but consistent with those observed in the inner regions of Milky Way and M51 \citep{Oka01a, Rosolowsky05a, Heyer09a, Hughes13b, Leroy15a, Rice16a}.  % also higher $P_{\rm int}$,
% which is $\propto\rho\sigma^2$
% M51: Colombo+14
However, clouds in nearby gas-rich galaxies are bigger in size (approximately an order of magnitude) and mass (approximately two orders of magnitude). 
These bigger clouds have been interpreted as a result of their higher gas mass fractions, surface densities, and velocity dispersions, 
since fragmentation occurs near the Jeans length $L_J\propto\sigma^2/\Sigma$ and 
Jeans mass $M_J\propto\sigma^4/\Sigma$ for dispersion-supported structures.

Based on the scaling of $M_J$\eq$\sigma^4/(G^2\Sigma)$ for the Jeans mass, a 
velocity dispersion of $\sigma\approx50$\,\kms and a 
gas mass surface density of $\Sigma_{\rm gas}\approx450$\,\Msun\,pc$^{-2}$ yields 
$M_J\sim$\,8\E{8}\,\Msun, which is in good agreement with the mass range found in the MCs identified (see \Fig{dist}).
%
Similarly massive molecular clouds have been reported in idealized closed-box isolated galaxy simulations done at higher resolution (e.g., a maximum 
resolution of 3\,pc in the 48\,kpc box studied by \citealt{Behrendt16a}). 
Note, however, that the IGM and merger and accretion histories are not properly modeled in such simulations since they adopt non-cosmological initial conditions. That said, this is reassuring --- our results are not far off in spite of the limited resolution ($l_{\rm cell}\approx$\,30\,pc).

%Note that regions of $Q\lesssim1$ is actually somewhat 
%less than the number of MCs we have identified based on density threshold --- 
%but this has something to do with the dependence on 
%$n_{\rm cut}$. The number of MCs and regions of low $Q$ are comparable if we only look at 
%MCs identified at the highest $n_{\rm cut}$.

% alpha parameters
As shown in \Fig{larsons_single}, 
the virial parameter of the sub-MCs is about $\alpha_{\rm vir}\gtrsim10$, which is considerably lower than their ``parent'' MCs found in the main disk of \flower ($\alpha_{\rm vir}\gtrsim100$).
%
For the MCs in the satellite galaxies, a lower virial parameter is found compared to the (sub-)MCs in the main disk of \flower, with $\alpha_{\rm vir}\approx$\,2.
Differences in their $\alpha_{\rm vir}$ most likely result from the weaker stellar feedback in the satellite galaxies as they have experienced less episodes of \SF compared to \flower (i.e., lower stellar-to-gas mass ratios of $\sim$0.1).

% pext
As shown in \Fig{larsons_single}, 
MCs in the main disk of \flower have higher pressure than the sub-MCs. The lower virial parameter and external pressure of the sub-MCs compared to their parent MCs are consistent with the notion that collapsing structures result from local gravitational instability within globally non-collapsing structures \citep[see e.g.,][]{Ballesteros-Paredes11a}, which are supported by turbulence and rotation on large scales.
%Based on the virial parameter, velocity dispersion, and pressure of the MC identified in the main disk of \flower,
%the MC itself is gravitationally unbound and supported by turbulence (from the feedback of multiple episodes of \SF)
%and galactic rotation on large scales. 
%% Turbulence in these substructures further dissipates in % e.g., shocks on even smaller scales, allowing sub-MCs to be bound and collapse.

For MCs in the satellite galaxies, we find even lower pressures and virial parameters, which are comparable to those found in clouds formed in the galactic disks  ($\alpha_{\rm vir}$\eq0.2$-$10; \citealt{Dobbs08a, Tasker09a}).
This suggests that MCs identified in the satellite galaxies are likely to be collapsing structures, and thus,\AP{i suspect a low or null \SF in the satellites, i.e. some of them should have $f_gas = 1$, i.e. no stars} \SF is expected to continue as gas from satellite galaxies is being accreted onto the main galaxies during the EoR.

 \DL{should probably move to somwehere later in this sec}
Maps of the Toomre $Q$ parameters for the gas, stars, and the effective two-component $Q_{\rm eff}$ are shown in \Fig{Qeff} 
(see also \Fig{h2density} for example of MCs identified in this evolutionary stage of \flower
using different $n_{\rm cut}$). Fragmentation are expected in regions of low Toomre $Q$ values.
Close resemblance of the $Q_{\rm eff}$ and $Q_{\star}$ maps indicates that contributions from the 
stellar component play an important role in 
governing the stability of the MCs against $m$\eq0 perturbations.
This can be understood since stars in \flower dominates the central part of the galaxy in mass, 
so their gravitational potential provides a non-negligible contribution to the stability. 
Similarly, contribution from the thickness of the disk is important in \flower since its disk is not thin (with a 
scale height to radius ratio of $h/r_{\rm gal}$\ssim150\,pc/1\,kpc\,$\simeq$\,0.15) and since \flower is more of a warped disk.
That is, some MCs are found in regions of $Q_{\rm gas}$\ssim1, which would suggest that they are gravitationally unstable;
however, when including the stabilizing effects due to its stellar potential and the 
thickness of its disk (via $\sigma_z$), some of these MCs are consistent with $Q_{\rm eff} > 1$.
This highlights the importance of accounting for stellar contribution and disk thickness when examining the stability of 
molecular gas structures, especially in the relatively evolved and enriched systems at high redshifts 
that are preferentially being imaged at high resolution with ALMA. One should be caution when interpreting results
based on gas-only Toomre $Q$ analysis.

@@

We thank Jens Kauffmann, Thushara Pillai, and Mark Swinbank for sharing their data.
%
TKDL acknowledges support by the NSF through award SOSPA4-009 from the NRAO and support from the Simons Foundation.
%
AF acknowledges support from the ERC Advanced Grant INTERSTELLAR H2020/740120.
%
This work is based on a project developed at the Kavli Summer Program in Astrophysics (KSPA) held at the Center for Computational Astrophysics of the Flatiron Institute in 2018. The program was co-funded by the Kavli Foundation and the Simons Foundation.
%
We thank the KSPA Scientific and Local Organizing Committees, and the program founder, Pascale Garaud, for supporting the genesis of this work.
%
We also thank the Center for Cosmology and Particle Physics at the New York University for their hospitality in hosting us after the steam pipe explosion in NYC during the KSPA.
%
This research has made use of NASA's Astrophysics Data System Bibliographic Services.
%
We acknowledge use of the Python programming language \citep{VanRossum1991}, Astropy \citep{astropy}, Cython \citep{behnel2010cython}, Matplotlib \citep{Hunter2007}, NumPy \citep{VanDerWalt2011}, \ncode{Pymses} \citep{Labadens2012}, SciPy \citep{scipyref}, and \ncode{yt} \citep{Smith09a,Turk11a}.
%
%and \ncode{yt}, a community-developed Python package for analyzing simulation data in Astronomy.
